Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-30 prop_letter.tex
prop_letter.tex \paragraph{Expectation Values for Quantum IVPMs} Use \sum to simplify the formula...
prop_iop.tex \section{Expectation Values for IVPMs} Updating...
prop_letter.tex Delete old Kochen-Specker theorem section...

Formally, we can ask: what can we deduce about the state of a quantum
system given a quantum interval-valued probability measure, i.e.,
given observations done with finite resources. Since the probabilities
are now intervals, it is intuitive to say a state~$\rho$ is consistent
with $\bar{\mu}$ on a projector~$P$ if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.

@@

Consider a quantum IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
for all $P\in\events$. This time, when we express the observable
as its spectral decomposition
\begin{equation}
\mathbf{O}=\sum_{i=1}^{N^{-}}\lambda_{i}^{-}P_{i}^{-}+\sum_{i=1}^{N^{+}}\lambda_{i}^{+}P_{i}^{+}\textrm{ ,}\label{eq:spectrum-decomposition}
\end{equation}
we separate the positive and negative eigenvalues and order its eigenvalues
from the smallest to the largest 
\begin{equation}
\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\textrm{ .}
\end{equation}
Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
with Eq.~(\ref{eq:quantum-expectation}) and define the expectation
value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
\begin{eqnarray}
\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{i=1}^{N^{+}}\lambda_{i}^{+}\left[\Delta\mul\left(P_{i}^{+\prime}\right),\Delta\mur\left(P_{i}^{+\prime}\right)\right]\nonumber \\
 &  & +\sum_{i=1}^{N^{-}}\lambda_{i}^{-}\left[\Delta\mul\left(P_{i}^{-\prime}\right),\Delta\mur\left(P_{i}^{-\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
\end{eqnarray}

@@

\begin{table*}
\caption{\label{table:commonBasis}In each row, three observables are listed
in the left column commutes, and their common eigenbasis is listed
in the right column. In order to unify and simplify the notation,
we do not normalize eigenstates, and represent the state~$\alpha_{00}\ket{00}+\alpha_{01}\ket{01}+\alpha_{10}\ket{10}+\alpha_{11}\ket{11}$
as $\left(\alpha_{00},\alpha_{01},\alpha_{10},\alpha_{11}\right)$.
Also, to simplify the notation further, the projector onto each eigenstate
used in Eq.~(\ref{eq:CEGA}) is named such that if two projectors
share the same index, they are commuting.}

\begin{ruledtabular}
\begin{tabular}{c|c}
Commuting observables & Common eigenbasis\tabularnewline
\hline 
$\begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
\sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
\sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}\\
\mathbb{1} & \otimes\sigma_{z} & \sigma_{x} & \otimes\mathbb{1} & \sigma_{x} & \otimes\sigma_{z}\\
\sigma_{z} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{z} & \otimes\sigma_{x}\\
\sigma_{z} & \otimes\sigma_{z} & \sigma_{x} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
\end{aligned}
$ & $\begin{aligned}(1,0,0,0) & \rightarrow P_{12} & (0,1,0,0) & \rightarrow P_{18} & (0,0,1,0) &  & (0,0,0,1) & \rightarrow P_{28}\\
(1,1,1,1) & \rightarrow P_{56} & (1,-1,1,-1) & \rightarrow P_{59} & (1,1,-1,-1) & \rightarrow P_{69} & (1,-1,-1,1)\\
(1,1,1,-1) & \rightarrow P_{37} & (1,1,-1,1) & \rightarrow P_{47} & (1,-1,1,1) &  & (-1,1,1,1) & \rightarrow P_{34}\\
(1,0,1,0) & \rightarrow P_{48} & (0,1,0,1) &  & (1,0,-1,0) & \rightarrow P_{58} & (0,1,0,-1) & \rightarrow P_{45}\\
(1,1,0,0) &  & (1,-1,0,0) & \rightarrow P_{67} & (0,0,1,1) & \rightarrow P_{17} & (0,0,1,-1) & \rightarrow P_{16}\\
(0,1,1,0) & \rightarrow P_{29} & (0,1,-1,0) & \rightarrow P_{23} & (1,0,0,1) & \rightarrow P_{39} & (1,0,0,-1)
\end{aligned}
$\tabularnewline
\end{tabular}
\end{ruledtabular}

\end{table*}

Since observables in Eq.~(\ref{eq:MerminSquare}) are not projections,
if we want to reformulate the above argument in the language of IVPMs,
we first need to find the common eigenbasis of each row and column,
and consider the projections to each eigenvectors~\cite{peres1995quantum,CabelloEstebaranzGarcia-Alcaine1996,Cabello_2008}.
Let $\mathcal{T}_{18}$ denote the named projectors onto eigenstates
listed in Table~\ref{table:commonBasis}, and the eigenstates they
project to are denoted by $\events_{18}$. The Kochen-Specker theorem
could then be proved by showing there is no function~$v:\events_{18}\rightarrow\left\{ 0,1\right\} $
satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}), where
\begin{equation}
\events_{18}=\set{\sum_{i=1}^{N}P_{i}}{\textrm{orthogonal }\left\{ P_{i}\right\} _{i=1}^{N}\subseteq\mathcal{T}_{18}}
\end{equation}
is a sub-event space.

Assume there is a function~$v:\events_{18}\rightarrow\left\{ 0,1\right\} $
satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}). There must be a
quantum IVPM~$\bar{\mu}:\events_{18}\rightarrow\mathscr{I}_{\mathrm{D}}$
defined by $\bar{\mu}\left(P\right)=\iota_{\mathrm{D}}\left(v\left(P\right)\right)$,
where 
\begin{equation}
\iota_{\mathrm{D}}\left(x\right)=\begin{cases}
\necess & \text{, if }x=1\text{ ;}\\
\imposs & \text{, if }x=0\text{ .}
\end{cases}\label{eq:homomorphism-0}
\end{equation}
For each the orthogonal basis in $\events_{18}$, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
gives the following equations: 
\begin{equation}
\begin{aligned}\necess & \subseteq\bar{\mu}\left(P_{12}\right)+\bar{\mu}\left(P_{18}\right)+\bar{\mu}\left(P_{17}\right)+\bar{\mu}\left(P_{16}\right)\textrm{ ,}\\
\necess & \subseteq\bar{\mu}\left(P_{16}\right)+\bar{\mu}\left(P_{67}\right)+\bar{\mu}\left(P_{69}\right)+\bar{\mu}\left(P_{56}\right)\textrm{ ,}\\
\necess & \subseteq\bar{\mu}\left(P_{56}\right)+\bar{\mu}\left(P_{59}\right)+\bar{\mu}\left(P_{58}\right)+\bar{\mu}\left(P_{45}\right)\textrm{ ,}\\
\necess & \subseteq\bar{\mu}\left(P_{45}\right)+\bar{\mu}\left(P_{48}\right)+\bar{\mu}\left(P_{47}\right)+\bar{\mu}\left(P_{34}\right)\textrm{ ,}\\
\necess & \subseteq\bar{\mu}\left(P_{34}\right)+\bar{\mu}\left(P_{37}\right)+\bar{\mu}\left(P_{39}\right)+\bar{\mu}\left(P_{23}\right)\textrm{ ,}\\
\necess & \subseteq\bar{\mu}\left(P_{23}\right)+\bar{\mu}\left(P_{29}\right)+\bar{\mu}\left(P_{28}\right)+\bar{\mu}\left(P_{12}\right)\textrm{ ,}\\
\necess & \subseteq\bar{\mu}\left(P_{28}\right)+\bar{\mu}\left(P_{18}\right)+\bar{\mu}\left(P_{58}\right)+\bar{\mu}\left(P_{48}\right)\textrm{ ,}\\
\necess & \subseteq\bar{\mu}\left(P_{47}\right)+\bar{\mu}\left(P_{37}\right)+\bar{\mu}\left(P_{17}\right)+\bar{\mu}\left(P_{67}\right)\textrm{ ,}\\
\necess & \subseteq\bar{\mu}\left(P_{69}\right)+\bar{\mu}\left(P_{59}\right)+\bar{\mu}\left(P_{39}\right)+\bar{\mu}\left(P_{29}\right)\textrm{ .}
\end{aligned}
\label{eq:CEGA}
\end{equation}
If we sum up the preceding equations, we will have
\begin{equation}
\left[9,9\right]\subseteq2\sum_{\ket{\psi}\in\mathcal{T}_{18}}\bar{\mu}\left(\ket{\psi}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Total}
\end{equation}
However, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Total})
can never be satisfied. Because each term in right-hand side is either
$\imposs=\left[0,0\right]$ or $\necess=\left[1,1\right]$, the right-hand
side is a singleton set of an even integer while the left-hand side
is $\left[9,9\right]$. Therefore, there is no quantum IVPM~$\bar{\mu}:\events_{18}\rightarrow\mathscr{I}_{\mathrm{D}}$.
Moreover, there is no quantum IVPM defined on the set of all projectors
as well; otherwise, if we have a quantum IVPM~$\bar{\mu}':\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
then we can restrict $\bar{\mu}'$ and define $\bar{\mu}=\left.\bar{\mu}'\right|_{\events_{18}}$.

>>>>

Formally, we can ask: what can we deduce about the state of a quantum
system given a quantum interval-valued probability measure, i.e.,
given observations done with finite resources. Since the probabilities
are now intervals, it is intuitive to say a state~$\rho$ is consistent
with $\bar{\mu}$ on a projector~$P$ if $\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
and denoted by $\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$.
Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means $\rho$
is consistent with $\bar{\mu}$ on every projector in $S$.

@@

Consider a quantum IVPM~$\bar{\mu}$ such that $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are the left-end and
the right-end of $\bar{\mu}$, respectively, i.e., $\bar{\mu}\left(P\right)=\left[\mul\left(P\right),\mur\left(P\right)\right]$
for all $P\in\events$. This time, when we express the observable
as its spectral decomposition
\begin{equation}
\mathbf{O}=\sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}P_{i}^{s}\textrm{ ,}\label{eq:spectrum-decomposition}
\end{equation}
we separate the positive and negative eigenvalues and order its eigenvalues
from the smallest to the largest 
\begin{equation}
\lambda_{N^{-}}^{-}\le\ldots\le\lambda_{1}^{-}\le0\le\lambda_{1}^{+}\le\ldots\le\lambda_{N^{+}}^{+}\textrm{ .}
\end{equation}
Let $P_{i}^{s\prime}=\sum_{j\ge i}P_{j}^{s}$ and $\Delta\mu^{*}\left(P_{i}^{s\prime}\right)=\mu^{*}\left(P_{i}^{s\prime}\right)-\mu^{*}\left(P_{i+1}^{s\prime}\right)$,
where $s\in\left\{ +,-\right\} $ and $\mu^{*}\in\left\{ \mul,\mur\right\} $.
We can combine the classical Choquet integral~\cite{Vitali1925,Choquet1954,GilboaSchmeidler1994,Grabisch2016}
with Eq.~(\ref{eq:quantum-expectation}) and define the expectation
value of $\mathbf{O}$ with respect to $\bar{\mu}$ as
\begin{eqnarray}
\expval{\mathbf{O}}_{\bar{\mu}} & = & \sum_{s\in\left\{ +,-\right\} }\sum_{i=1}^{N^{s}}\lambda_{i}^{s}\left[\Delta\mul\left(P_{i}^{s\prime}\right),\Delta\mur\left(P_{i}^{s\prime}\right)\right]\textrm{ .}\label{eq:quantum-interval-expectation}
\end{eqnarray}

@@
